Large-scale feature selection with Gaussian mixture models for remote sensing images

### 2016-10-14 paper.tex
correct table

            GMM SFS kappa & 257             & 496             & 955             & {\bfseries 7.7} & {\bfseries 8.6} & {\bfseries 8.7} \\
            GMM SFS JM &    {\bfseries 8.6} & {\bfseries 8.9} & {\bfseries 9.1} & {\bfseries 9.7} & {\bfseries 9.8} & {\bfseries 9.6} \\
            GMM SFFS JM &   {\bfseries 8.8} & {\bfseries 9.0} & {\bfseries 9.3} & {\bfseries 9.7} & {\bfseries 9.8} & {\bfseries 9.8} \\
            GMM ridge &     71.7            & 105             & 167             & 530 & 530 & 530 \\
            KNN &           {\bfseries 8.9} & 19.6            & 59.7            & 387 & 639 & 887 \\
            Random Forest & 24.5            & 49.3            & 105             & 33.0 & 41.7 & 45.9 \\
            \bottomrule
        \end{tabularx}
    \end{table}

>>>>

            GMM SFS kappa & 257             & 496             & 955             & {\bfseries 5.2} & {\bfseries 5.2} & {\bfseries 5.5} \\
            GMM SFS JM &    {\bfseries 8.6} & {\bfseries 8.9} & {\bfseries 9.1} & {\bfseries 5.7} & {\bfseries 5.7} & {\bfseries 5.9} \\
            GMM SFFS JM &   {\bfseries 8.8} & {\bfseries 9.0} & {\bfseries 9.3} & {\bfseries 5.0} & {\bfseries 5.0} & {\bfseries 5.4} \\
            GMM ridge &     71.7            & 105             & 167             & 530 & 530 & 530 \\
            KNN &           {\bfseries 8.9} & 19.6            & 59.7            & 387 & 639 & 887 \\
            Random Forest & 24.5            & 49.3            & 105             & 33.0 & 41.7 & 45.9 \\
            \bottomrule
        \end{tabularx}
    \end{table}
